Convex Surrogates via Polyhedral Losses

### 2019-05-08 notes/bo-separated.tex
attempted update to proof

We are given an original loss $\ell$ with property $\gamma$ and finite report space $\R$; and a polyhedral embedding with loss $L$, property, $\Gamma$, and embedding points $\{u_r : r \in \R\}$.

For each report $r \in \R$, let $u_r$ denote its embedding point.

@@

@@

  Now, we apply the following iterative procedure.
  For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-separated}).
  For every $u \in B\left(U, \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.

@@

  Finally, we must show that $\psi$ is a separated, calibrated link.
  \bo{TODO}
\end{proof}

>>>>

We are given an original loss $\ell$ with property $\gamma$ and finite report space $\R$; and a polyhedral embedding with loss $L$, property, $\Gamma$, report space $\R' \subseteq \reals^d$, and embedding points $\{u_r : r \in \R\}$.

@@

\begin{lemma} \label{lemma:distance-loss}
  If $L$ is a polyhedral loss, there exists a constant $c$ such that:
  For any $p$, if the set $U$ is optimal with expected loss $z$, and $d(U,u) \geq \delta$, then $L(u;p) > z + c\delta$.
\end{lemma}
\begin{proof}
  \bo{TODO}
\end{proof}

@@

  Now, we apply the following iterative procedure.
  For each $R \in \mathcal{S}$, consider the corresponding set $U \in \mathcal{U}$ (given by the bijection of Lemma \ref{lemma:U-biject}).
  For every $u \in B\left(U, \epsilon\right)$, we set $\Psi(u) = \Psi(u) \cap R$.

@@

  Finally, we must show that $\psi$ is a separated, calibrated link.
  It is calibrated because each $U$ maps under $\psi$ into the corresponding $R$ (since its entire thickening does).
  For separation, fix $p$. Now, suppose $U$ is optimal and $u$ is not.
  Now, if $u$ does not map to an optimal report, then it is not in $B(U,\epsilon)$.
  So by Lemma \ref{lemma:distance-separated}, its expected loss is at least $c\epsilon$ larger than optimal for some $c$ depending only on $L$.
  This holds for all such $u$, so the link is separated.
\end{proof}
